Diversity dynamics in Nymphalidae butterflies: Effect of phylogenetic uncertainty on diversification rate shift estimates

### 2015-01-14 response_to_reviewers.tex

\textbf{30. Response:}
\begin{quote}
\color{blue}
We reworded the sentence and now we recommend using MultiMEDUSA.
\end{quote}

\textbf{31. Reviewer's Comment:}
Page 10, second full paragraph: the results described here (rate increase in 
Ithomiini \& Charaxes, rate decrease in Danaina) are incongruent with those
described on page six (four rate increases). This incongruence needs to be 
addressed.

\textbf{31. Response:}
\begin{quote}
\color{blue}
We revised the paragraph and included the two other increases
in diversification rate: \emph{Ypthima} and the clade \emph{Callicore} + 
\emph{Diaethria}
\end{quote}

\textbf{32. Reviewer's Comment:}
Page 10, second full paragraph, second sentence: replace “splits” with “shifts”.

\textbf{32. Response:}
\begin{quote}
\color{blue}
We replaced the word according to the reviewer's suggestion:
\end{quote}

\textbf{33. Reviewer's Comment:}
Page 10, second full paragraph, third sentence: 2 changes; (A) replace “the
trait 'feeding on Solanaceae'” to “Solanaceae-feeding”; (B) add qualifier
“likely”: “was likely important in the diversification...”

\textbf{33. Response:}
\begin{quote}
\color{blue}
We revised the paragraph according to the reviewer's suggestions.
\end{quote}

### 2015-01-14 MS_revised.tex
comment 33

Our MultiMEDUSA approach to perform analyses on the posterior
distribution of trees found strong support for an increase in net
diversification rate in the tribe Ithomiini, the genera \emph{Ypthima},
\emph{Charaxes}, the clade \emph{Callicore} + \emph{Diaethria} and for a
decrease in net diversification rate in the
subtribe Danaina. Due to phylogenetic uncertainty, we did not obtain
strong support for other diversification shifts in Nymphalidae. Our
BiSSE analysis corroborated other studies in that the trait ``feeding on
Solanaceae'', or a codistributed character, was important in the
diversification of Ithomiini butterflies. However, by applying MEDUSA we
found that a critical character in the radiation of the group might have
appeared after the shift from Apocynaceae to Solanaceae. We also found
that the trait ``feeding on Apocynaceae'' is not responsible for the
slowdown of diversification in Danaina. Ithomiini and Solanaceae
diversified near simultaneously, which is in agreement with the diffuse
cospeciation hypothesis \cite{nyman2012, janz2011}.

>>>>

Our MultiMEDUSA approach to perform analyses on the posterior
distribution of trees found strong support for an increase in net
diversification rate in the tribe Ithomiini, the genera \emph{Ypthima},
\emph{Charaxes}, the clade \emph{Callicore} + \emph{Diaethria} and for a
decrease in net diversification rate in the
subtribe Danaina. Due to phylogenetic uncertainty, we did not obtain
strong support for other diversification shifts in Nymphalidae. Our
BiSSE analysis corroborated other studies in that Solanaceae-feeding,
or a codistributed character, was likely important in the
diversification of Ithomiini butterflies. However, by applying MEDUSA we
found that a critical character in the radiation of the group might have
appeared after the shift from Apocynaceae to Solanaceae. We also found
that the trait ``feeding on Apocynaceae'' is not responsible for the
slowdown of diversification in Danaina. Ithomiini and Solanaceae
diversified near simultaneously, which is in agreement with the diffuse
cospeciation hypothesis \cite{nyman2012, janz2011}.
